Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-16 VMCAI-revised-version/final.tex
up
effectivity

In the case
of an ideal-effective (upward compatible) WSTS, {\sc Resilience} is undecidable.

\begin{theorem}\label{indec WSTS with dcs}
{\sc Resilience} for ideal-effective $\omega^2$-WSTS with strong compatibility and for downward closed set $\Safe$ is undecidable.
\end{theorem}

@@

Remark that
Theorem~\ref{SL Lossy} and
Theorem~\ref{SL int-VASS}
(resp. Theorem~\ref{RP VASS})
did not make use of the hypothesis that $\Bad$ is the complement of $\Safe$, simply relying on the
semilinearity of the set (resp. its definability in the existential theory of the rationals with addition and order). Thus 
the mentionned theorems still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.

>>>>

In the case of (upward compatible) WSTS with ideally-effectivity, {\sc Resilience} is undecidable.

\begin{theorem}\label{indec WSTS with dcs}
{\sc Resilience} for ideally-effective $\omega^2$-WSTS with strong compatibility and for downward closed set $\Safe$ is undecidable.
\end{theorem}

@@

Remark that
Theorem~\ref{SL Lossy} 
(resp. Theorem~\ref{RP VASS})
did not make use of the hypothesis that $\Bad$ is the complement of $\Safe$, simply relying on the
semilinearity of the set (resp. its definability in the existential theory of the rationals with addition and order). Thus 
the mentionned theorems still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.
